---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## WeibullR.plotly

WeibullR.plotly is a simple R package for building interactive Weibull Probability Plots. This package depends on WeibullR, a R package for Weibull analysis, and plotly, an interactive web-based graphing library.

To view an interactive version of this ReadMe, visit [https://rpubs.com/paulgovan/WeibullRplotlyReadMe](https://rpubs.com/paulgovan/WeibullRplotlyReadMe)

## Getting Started 

WeibullR.plotly is still in development. To install the developmental version in R:

```{r, eval=FALSE}
devtools::install_github('paulgovan/weibullr.plotly')
```

## Basic Examples

To build a probability plot, first fit a `wblr` object using the `WeibullR` package and then use `plotly_wblr` to build the plot.

```{r message=FALSE, warning=FALSE}
library(WeibullR)
library(WeibullR.plotly)
failures<-c(30, 49, 82, 90, 96)
obj<-wblr.conf(wblr.fit(wblr(failures)))
plotly_wblr(obj)
```

To build a contour plot, use the `plotly_contour` function. Note that contour plots are only available where `method.fit='mle'` and `method.conf='lrb'`.

```{r message=FALSE, warning=FALSE}
obj<-wblr.conf(wblr.fit(wblr(failures), method.fit = 'mle'), method.conf = 'lrb')
plotly_contour(obj)
```

## Customization

WeibullR.plotly has several customization options.

```{r message=FALSE, warning=FALSE}
plotly_wblr(obj, main='Weibull Probability Plot', xlab='Years', ylab='Failure Probability', col='blue', signif=4, grid=FALSE)
```

```{r message=FALSE, warning=FALSE}
plotly_contour(obj, main='Weibull Contour Plot', col='red', signif=4, grid=FALSE)
```

## More Examples

For more examples with WeibullR.plotly, visit [https://rpubs.com/paulgovan/WeibullRplotlyExamples](https://rpubs.com/paulgovan/WeibullRplotlyExamples)
