---
title: "Reliability Growth Analysis"
output: 
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{rga}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To run a Reliability Growth Analysis, start by loading `ReliaGrowR` and `WeibullR.plotly`

```{r setup, warning=FALSE}
library(ReliaGrowR)
library(WeibullR.plotly)
```

## Crow-AMSAA Model

To run a Crow-AMSAA model, first set up some cumulative time and failure data:
```{r}
times <- c(100, 200, 300, 400, 500)
failures <- c(1, 2, 1, 3, 2)
```

Then run the rga and plot the results:
```{r}
result <- rga(times, failures)
plotly_rga(result)
```

## Piecewise Weibull NHPP Model

To run a Piecewise Weibull NHPP, first set up some cumulative time/failure data and specify the breakpoint:
```{r}
times <- c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000)
failures <- c(1, 2, 1, 1, 1, 2, 3, 1, 2, 4)
breakpoints <- 400
```

Then run the rga and plot the results:
```{r}
result <- rga(times, failures, model_type = "Piecewise Weibull NHPP", breakpoints = breakpoints)
plotly_rga(result, fitCol = "blue", confCol = "blue", breakCol = "red")
```

## Duane Model

To run a Duane Model, first set up some cumulative time and failure data:
```{r}
times <- c(100, 200, 300, 400, 500)
failures <- c(1, 2, 1, 3, 2)
```

Then plot the results:
```{r}
fit <- duane_plot(times, failures, plot = FALSE)
plotly_duane(fit, fitCol = "darkgreen")
```

